\documentclass[12pt]{article}

\begin{document}

\section*{Firefox OS Asynchronous Request}
In Firefox OS, app is treated as web page. Web apps need to access device hardware (such as battery status or the device vibration hardware), as well as access to data stored on the device (such as the calendar or contacts list). This is achieved via WebAPI. % introduce WebAPI

Most WebAPIs need to send an asynchronous request to access device resource. We use contacts API as an example. When app demands contact from contacts list,  it calls contacts API and registers onsuccess and onerror callback handlers which are the callback functions to handle response of the API call. % call asynchronized WebAPI

Contacts API generates a random ID for the request and store request which is a DOMRequest object in a list. DOMRequest object contains the search result from contacts list as well as a reference to operation's result. Additionally, in order to identify which frame sends the request, DOMRequest object includes DOMWindow which is created for each frame. After random ID generated, Contacts API sends get-contact request to system and return a dummy DOMRequest object which may be assigned  search result in the future to caller.  % send request
When Contacts API receives the response of API call, Firefox OS uses same ID to retrieve the DOMRequest Object which send get-contact request from list. DOMRequest Object can be assigned contact information only if the reference of DOMRequest still comes from same domain.   % receive response

\end{document}
